Randomized trace estimation for parameter-dependent matrices applied to spectral density approximation

### 2024-06-27 paper/re-pro-badge.tex
automatically reproduce paper

This document, along with all included plots and tables, was generated from commit \href{https://github.com/FMatti/Rand-SD/tree/ca391a8}{ca391a8} at \href{https://github.com/FMatti/Rand-TRACE}{github.com/FMatti/Rand-TRACE} on 2024-02-05 at 18:44:29 UTC.

>>>>

This document, along with all included plots and tables, was generated from commit \href{https://github.com/FMatti/Rand-SD/tree/ca391a8}{ca391a8} at \href{https://github.com/FMatti/Rand-TRACE}{github.com/FMatti/Rand-TRACE} on 2024-02-05 at 18:44:29 UTC.This document, along with all included plots and tables, was generated from commit \href{https://github.com/FMatti/Rand-TRACE/tree/4cf9b6b}{4cf9b6b}}} at \url{https://github.com/FMatti/Rand-TRACE}}} on 2024-06-27 at 15:01:59 UTC.
